\chapter{Contents of Submitted DVD}
  A DVD was submitted to accompany this report consisting of supporting material for the project. Below is an outline of the file structure of the disk as well as a description of the material.
  
  \begin{itemize}
    \item \textbf{Folder - \mintinline{js}{cad}:} A complete, packed set of files containing the entire 3D CAD design.
    \item \textbf{Folder - \mintinline{js}{media}:}
      \begin{itemize}
        \item \textbf{Folder - \mintinline{js}{renders}:} 3D renders of the completed rover model rendered in the 3D CAD software used for the project.
        \item \textbf{Folder - \mintinline{js}{images}:} Images of the completed rover model.
        \item \textbf{Folder - \mintinline{js}{screenshots}:} Screenshots of the completed RSVP Client user interface.
      \end{itemize}
    \item \textbf{Git Repository - \mintinline{js}{mars-rover-writeup}:} The \LaTeX~source for this report. Also available online at \url{https://github.com/WoodyWoodsta/mars-rover-rce/tree/thesis}.
    \item \textbf{Folder - \mintinline{js}{software}:} Note that the versions of the software in the repositories listed below are available as a frozen version on the \mintinline{js}{thesis} branch. Continued development of the software is kept on other branches including \mintinline{js}{master}.
      \begin{itemize}
        \item \textbf{Git Repository - \mintinline{js}{mars-rover-rce}:} The software project and source used for the RCE. Also available online at \url{https://github.com/WoodyWoodsta/mars-rover-rce/tree/thesis}.
        \item \textbf{Git Repository - \mintinline{js}{mars-rover-rsvp-server}:} The software project and source used for the RSVP Server. Also available online at \url{https://github.com/WoodyWoodsta/mars-rover-rsvp-server/tree/thesis}.
        \item \textbf{Git Repository - \mintinline{js}{mars-rover-rsvp-client}:} The software project and source used for the RSVP Client. Also available online at \url{https://github.com/WoodyWoodsta/mars-rover-rsvp-client/tree/thesis}.
      \end{itemize}
    \item \textbf{File - \mintinline{js}{mars-rover-writup.pdf}:} This report, in PDF format.
    \item \textbf{File - \mintinline{js}{mars-rover-demonstration.mp4}:} A demonstration video showing some of the tests performed on the final rover model.
  \end{itemize}